---
title: "500-gtseq-panel"
author: "Mac Campbell"
date: "7/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

## Primers

A list of sites included in the GTSeq panel was sent out by J. von Bargen on 07/10/2022. Reading in as .tsv

```{r}
sites<-read_tsv("meta/status-round3.tsv")
sites %>% group_by(Status) %>% summarize(Count=n())
```


Sitelist includes genotypes, hybridization assay sites and parentage SNPS.

```{r}
geno<-sites[str_starts(sites$Loci, "lg|scaffold"),] %>% filter(Status=="KEEP")
hybr<-sites[str_starts(sites$Loci, "DSM|LFS|WKS"),] %>% filter(Status=="KEEP")
padr<-sites[str_starts(sites$Loci, "Htr-GVL"),    ] %>% filter(Status=="KEEP")

#Should sum to 415
length(geno$Loci)+length(hybr$Loci)+length(padr$Loci)
```

## Corresponding Sites

_1_ Genotypes       
These should be the same as the file, just need to check naming against plink file. Plink file looks like this "lg01 lg01_150209 0 150209", we have "lg01-site-xxxxxx"

```{r}
genos<-tidyr::separate(geno, Loci, into=c("Chrom","Null","Site"), sep="-", remove=FALSE, extra="drop") %>% select(-Null) %>%
  mutate(Plink=paste0(Chrom, "_", Site))
genos
```

_2_ Hybridization     
I aligned via blast, and some of them were invariant in DSM as expected, and won't be in the genotype file.     
Should expect these two.     
1 WKS_04 8426928 8427685 lg07    8427639 A     G     PR;MAF 0.120061     
2 WKS_07  728701  729080 lg08     728783 T     A     PR;MAF 0.25627      

```{r}
v1<-c("WKS_04","WKS_07")
v2<-c("lg07","lg08")
v3<-c("8427639","728783")

hybrs<-cbind(v1,v2,v3) %>% as_tibble() %>% rename(Loci=v1, Chrom=v2, Position=v3) %>% mutate(Plink=paste0(Chrom, "_", Position)) %>% mutate(Status="Keep") %>% select(Loci, Status, Plink)
hybrs
```


_3_ Parentage SNPS
These should be in our set.  Let's pull, using a less stringent set bc some of these didn't pass the filters.     
```{r}
assay<-read_csv("outputs/400/parentage-matches-light-filter-bcftools.csv") %>% select(query, target, Position, Start, End) %>% separate(query, into=c("Name1","Name2"), sep=",")
# Only know some of the positions, so left_join this way
# Some are duplicated

padrs<-left_join(padr, assay, by=c("Loci"="Name1")) %>% mutate(Plink=paste0(target, "_", Position))
padrs
```

Combine!

```{r}
total<-bind_rows(select(genos, Loci, Status, Plink), hybrs, select(padrs, Loci, Status, Plink))
write_tsv(select(total,Plink), col_names = FALSE, "meta/round3-snps.tsv")
total
```

## Calc LD

Now, I can calculate ld with plink. in `(base) maccamp@farm:~/dsm-genotyping/outputs/500$`     


